---
title: Job Industry Classification
author:
  - name: Jiancong Qi
    affil: 1
  - name: Jinyi Li
    affil: 1
  - name: Joy Wang
    affil: 1
  - name: Zheng Wang
    affil: 1
  - name: Wenxin Zhou
    affil: 1
affiliation:
  - num: 1
    address: Department of Statistics, UCLA
# - num: 2
#   address: Some other affiliation
column_numbers: 3
font_family: Helvetica
primary_colour: "#2774AE"
secondary_colour: "#FFD100"
accent_colour: "#003B5C"
affiliation_textcol: "#FFD100"
logoright_name: https&#58;//raw.githubusercontent.com/brentthorne/posterdown/master/images/betterhexlogo.png
logoleft_name: http&#58;//www.firststar.org/wp-content/uploads/2015/02/ucla1.jpg
## https://ev0awwmgj4-flywheel.netdna-ssl.com/wp-content/uploads/images/products/products-University-of-CA-Los-Angeles-Seal.jpg
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: packages.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Introduction

In this poster, we demonstrate a practice of industry classifications with job descriptions. In the dataset of the DataFest 2018, around 90% of the job postings do not have industry information. Using the words in the job description, we try to classify the job postings without industry information to different industries. 

## Objectives

Build model to perform job industry classification

# Methods

1.Seperate the job postings with industry information into training and testing sets.
2.Extra and split every word in the industry and title column with NAs removed
3.Based on the word list, create an industry and title word dictionary
4.


# Results


# Next Steps



# Conclusion



```{r, include=FALSE}
knitr::write_bib(c('knitr','rmarkdown','posterdown','pagedown'), 'packages.bib')
```

# References
